Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-07-09 msbr_reproc.tex
rephrasing in online reprocessing method section

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\captionsetup[table]{
        labelsep = newline,
        name = TABLE, justification=justified,
        singlelinecheck=false,%%%%%%% a single line is centered by default
        labelsep=colon,%%%%%%
skip = \medskipamount}
\begin{table}[h!]
        %\centering
        \begin{tabular}{p{0.46\linewidth} p{0.50\linewidth}} \toprule
                Thermal capacity of reactor           & 2250 MW(t)
                \\ \midrule
                %Net electrical output                 & 1000 MW(e) \\ \midrule
                %Net thermal efficiency        & 44.4\%
                %\\ \midrule
                Volume fraction of salt in central core zone     & 0.132
                \\ \midrule
                Volume fraction of salt in outer core zone       & 0.37
                \\ \midrule
                Fuel-salt inventory (Zone I)                  & 8.2 m$^3$	
                \\ \midrule
                Fuel-salt inventory (Zone II)                 & 10.8 m$^3$	
                \\ \midrule
                Fuel salt components                  & 
                LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$-$^{239}$PuF$_3$	\\ 
                \midrule
                Fuel salt composition                 & 
                71.767-16-12-0.232-0.0006 mole\%
                \\
                \bottomrule
        \end{tabular}
        \caption{Summary of principal data for MSBR.}
        \label{tab:data}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \gls{MSBR} core consists of two different zones. The central 
zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 
The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 
2 safety rods consisting of boron carbide clad. The under-moderated zone, Zone 
II, with 37\% fuel salt, and radial reflector, surrounding the more active 
portion serves to diminish neutron leakage from the reactor core. In this work, 
only a Zone I element with a $3.42138 cm$ diameter central fuel channel and molten-salt 
fuel volume fraction of 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
geometry of the unit cell model. The boundary condition of the unit cell is 
periodic. The density of the fuel salt is $3.3304 \frac{g}{cm^3}$ and the graphite density is 
$1.843 \frac{g}{cm^3}$. The temperature of fuel and graphite is fixed at 908K for the whole 
reprocessing cycle\cite{robertson_conceptual_1971}.

\begin{figure}[h] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=0.90\linewidth]{zone_I_mesh.png}
        \caption{MSBR unit cell of Zone I geometry.}
        \label{fig:zoneI}
\end{figure}

\subsection{Online reprocessing method}

Currently, researchers usually using supporting tools and scripts to simulate 
online reprocessing and refueling. Most researchers investigating the 
\glspl{MSR} have utilised for reprocessing calculations stochastic (i.e. 
\gls{MCNP}) or deterministic (i.e. SCALE) code with originally-developed 
scripts based on Python \cite{jeong_equilibrium_2016,park_whole_2015}. The 
Serpent 2 is the first code supporting continuous material reprocessing, and 
allows create needed number of material flows into the fuel and/or out from the 
fuel.

>>>>

\usepackage{tabularx} % for nice wrapping of table text

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\captionsetup[table]{
        labelsep = newline,
        name = TABLE, justification=justified,
        singlelinecheck=false,%%%%%%% a single line is centered by default
        labelsep=colon,%%%%%%
skip = \medskipamount}
\begin{table}[h!]
        %\centering
        %\begin{tabular}{p{0.46\linewidth} p{0.50\linewidth}} \toprule
        \begin{tabularx}{\linewidth}{l X} \toprule 
                Thermal capacity of reactor           & 2250 MW(t)
                \\ \midrule
                %Net electrical output                 & 1000 MW(e) \\ \midrule
                %Net thermal efficiency        & 44.4\%
                %\\ \midrule
                Salt volume fraction in central core zone     & 0.132
                \\ \midrule
                Salt volume fraction in outer core zone       & 0.37
                \\ \midrule
                Fuel-salt inventory (Zone I)                  & 8.2 m$^3$	
                \\ \midrule
                Fuel-salt inventory (Zone II)                 & 10.8 m$^3$	
                \\ \midrule
                Fuel salt components                  & 
                LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$-$^{239}$PuF$_3$	\\ 
                \midrule
                Fuel salt composition                 & 
                71.767-16-12-0.232-0.0006 mole\%
                \\
                \bottomrule
        \end{tabularx}
        \caption{Summary of principal data for MSBR.}
        \label{tab:data}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The \gls{MSBR} core consists of two different zones. The central 
zone, Zone I, in which 13.2\% of the volume is fuel salt and 86.8\% graphite. 
The first zone is composed of 1320 graphite cells, 2 graphite control rods, and 
2 safety rods consisting of boron carbide clad. The under-moderated zone, Zone 
II, with 37\% fuel salt, and radial reflector, surrounding the more active 
portion serves to diminish neutron leakage from the reactor core. In this work, 
only a Zone I element with a $3.42138 cm$ diameter central fuel channel and molten-salt 
fuel volume fraction of 0.132 was considered. Figure~\ref{fig:zoneI} shows the 
geometry of the unit cell model. The boundary condition of the unit cell is 
periodic. The density of the fuel salt is $3.3304 g/cm^3$ and the graphite density is 
$1.843 g/cm^3$. The temperature of fuel and graphite is fixed at 908K for the whole 
reprocessing cycle\cite{robertson_conceptual_1971}.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=0.90\linewidth]{zone_I_mesh.png}
        \caption{MSBR unit cell of Zone I geometry.}
        \label{fig:zoneI}
\end{figure}

\FloatBarrier
\subsection{Online reprocessing method}

Currently, researchers 
investigating the \glspl{MSR} 
typically develop custom supporting tools and scripts to simulate 
online reprocessing and refueling. Most utilize stochastic (i.e. 
\gls{MCNP}) or deterministic (i.e. SCALE) methods for depletion and supplement 
these with custom Python scripts to capture the impacts of reprocessing 
\cite{jeong_equilibrium_2016,park_whole_2015}. Serpent 2 is the 
first commonly used monte carlo software to support continuous material 
reprocessing. It does so by allowing the user to 
create multiple material flows into and out of the fuel.
